DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-10 child_single_geo_in_region.Rmd
shift the regions to loops and nest child

```{r, results = 'asis', eval=!has_roads}
cat("This area does not have either known roads.")
```

@@

```{r, eval=has_both}
# identified a mislabeled RD_LOG_ID in the sidewalk data for Madrone (as Main)
x <- st_as_sf(this_sw_sh) %>% mutate(LENGTH = as.integer(LENGTH)) %>% filter(RD_LOG_ID == 49435 & LENGTH > 1000)
x$RD_LOG_ID <- 43809
# x will have 0 rows if we are not dealing with Manchester

@@

# this_centerline_miles is CENTERLINE MILES TOTAL
this_centerline_miles <- format(round(as.numeric(sum(st_length(this_roads))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_sw/sh_miles is RIGHT LEFT MILES with SW or SH TOTAL
this_sw_sh_miles <- format(round(as.numeric(sum(st_length(this_sw_sh))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_sw/sh_miles is RIGHT LEFT MILES where we could match SW/SH to a road segment
this_comb_miles <- format(round(as.numeric(sum(st_length(this_comb))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
this_msg <- ifelse(this_comb_miles > this_sw_sh_miles, 
                   "There are duplicate segments matching.", 
                   "")

# ggplot() +
#   geom_sf(data = this_geo, aes(fill = 1), alpha = 0.2, lwd = 0, show.legend = FALSE) + 
#   geom_sf(data = st_buffer(bind_rows(this_sw_sh, x), 50, endCapStyle="FLAT"),
#           fill = "#4E22EE", alpha = 0.5) +
#   geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
#   geom_sf(data = this_test2, color = "black") +
#   geom_sf(data = this_sw_sh, aes(color = as.factor(RD_LOG_ID)), lwd = 0)

@@

```{r, eval=has_both}
 # should we test for points?
the_points <- c()
if (exists("the_schools")) { the_points <- append(the_points, "the_schools")} 
if (exists("the_libraries")) { the_points <- append(the_points, "the_libraries")} 
if (exists("the_transits")) { the_points <- append(the_points, "the_transits")} 
check_points <- ifelse(length(the_points) > 0, T, F)
has_point = FALSE # start with false
```

```{r, eval=has_both & check_points}
  # see if this geo has a point (is it an area around a place, like a school)

if (length(which(eval(as.symbol(the_points)) == this_geo$tomatch)) !=0) {
  # we need to figure out which one
  has_point = TRUE
  tr <- which(eval(as.symbol(the_points)) == this_geo$tomatch)
  if (tr <= length(the_schools)) { # it is a school
    this_point <- st_as_sf(pub_schools) %>%
      filter(NAME == this_geo$tomatch)
  } else if (tr > length(the_schools) & 
             tr <= length(the_schools) + length(the_libraries)) { # library
    this_point <- st_as_sf(libraries) %>%
      filter(NAME == this_geo$tomatch)
  } else { #transit
    this_point <- st_as_sf(transit_cp) %>%
      filter(NAME == this_geo$tomatch)
  }
}

@@

p1 <- kitsap +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.5, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) +
  geom_sf(data = this_sw_sh, aes(color = as.factor(TYPE)), show.legend = "line") + 
  sw_sh_col +
  theme_void() +
  labs(title = "{{current_geo}}",#paste("Map for","{{current_geo}}"),
       color = "Pedestrian Facilities")

r <- ggplot() +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.4, lwd = 0, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
  geom_sf(data = filter(this_sw_sh, SIDE_OF_RO == "RIGHT"), aes(color = as.factor(TYPE))) +
  {if(has_point) geom_sf(data = this_point, 
                         aes(color = 1), color = "black", show.legend = FALSE)} +
  sw_sh_col +
  labs(title = "Right",
       color = "Pedestrian Facilities") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))

l <- ggplot() +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.4, lwd = 0, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
  geom_sf(data = filter(this_sw_sh, SIDE_OF_RO == "LEFT"), aes(color = as.factor(TYPE))) +
  {if(has_point) geom_sf(data = this_point, 
                         aes(color = 1), color = "black", show.legend = FALSE)} +
  sw_sh_col +
  labs(title = "Left",
       color = "Pedestrian Facilities") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))

@@

((p1 + 
  plot_layout(guides = 'collect') +
  labs(color = "Pedestrian Facilities") & 
    theme(legend.position = "bottom") &
    guides(color=guide_legend(nrow=this_rows,byrow=TRUE))) +
  (l + theme(legend.position = "none") ) +
  (r + theme(legend.position = "none") ) )

>>>>

```{r, results = 'asis', eval=!has_roads}
cat("This area does not have known roads.")
```

@@

```{r, eval=has_both}
# identified a mislabeled RD_LOG_ID in the sidewalk data for Madrone (as Main)
x <- st_as_sf(this_sw_sh) %>% mutate(LENGTH = as.integer(LENGTH)) %>% filter(RD_LOG_ID == 49435 & LENGTH > 500)
x$RD_LOG_ID <- 43809
# x will have 0 rows if we are not dealing with Manchester

@@

# this_centerline_miles is CENTERLINE MILES TOTAL
this_centerline_miles <- format(round(as.numeric(sum(st_length(this_roads))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_sw/sh_miles is RIGHT LEFT MILES with SW or SH TOTAL
this_sw_sh_miles <- format(round(as.numeric(sum(st_length(this_sw_sh))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
# this_sw/sh_miles is RIGHT LEFT MILES where we could match SW/SH to a road segment
this_comb_miles <- format(round(as.numeric(sum(st_length(this_comb))/5280), 1), 
                           digits = 1, nsmall=1, big.mark=",")
this_msg <- ifelse(this_comb_miles > this_sw_sh_miles, 
                   "There are duplicate segments matching.", 
                   "")
```

@@

```{r, eval=has_both & has_points}
  # see if this geo has a point (is it an area around a place, like a school)
this_point <- st_as_sf(b_pointdf) %>%
      filter(NAME == this_geo$tomatch)
```

@@

p1 <- kitsap +
  geom_sf(data = this_geo, aes(fill = 1), lwd = 0, alpha = 0.8, show.legend = FALSE) +
  #geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) +
  geom_sf(data = this_sw_sh, aes(color = as.factor(TYPE)), show.legend = "line") + 
  sw_sh_col +
  theme_void() +
  labs(title = "{{current_geo}}",#paste("Map for","{{current_geo}}"),
       color = "")

r <- ggplot() +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.4, lwd = 0, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
  geom_sf(data = filter(this_sw_sh, SIDE_OF_RO == "RIGHT"), aes(color = as.factor(TYPE))) +
  {if(has_points) geom_sf(data = this_point, 
                         aes(color = 1), color = "black", show.legend = FALSE)} +
  sw_sh_col +
  labs(title = "Right",
       color = "") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))

l <- ggplot() +
  geom_sf(data = this_geo, aes(fill = 1), alpha = 0.4, lwd = 0, show.legend = FALSE) +
  geom_sf(data = this_roads, aes(color = 1), color = "#999999", alpha = 0.5) + 
  geom_sf(data = filter(this_sw_sh, SIDE_OF_RO == "LEFT"), aes(color = as.factor(TYPE))) +
  {if(has_points) geom_sf(data = this_point, 
                         aes(color = 1), color = "black", show.legend = FALSE)} +
  sw_sh_col +
  labs(title = "Left",
       color = "") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))

@@

((p1 + 
  plot_layout(guides = 'collect') +
  labs(color = "") & 
    theme(legend.position = "bottom") &
    guides(color=guide_legend(nrow=this_rows,byrow=TRUE))) +
  (l + theme(legend.position = "none") ) +
  (r + theme(legend.position = "none") ) )
